---
title: "Chapter3.Lab"
author: "Guihong Wan"
date: "7/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

MASS is a large collection of data set and functions, like Boston data set.
Boston records medv(median house value) for 506 neighborhoods around Boston.

```{r}
library(MASS)
```

ISLR includes the data sets
```{r}
library(ISLR)
```
#Simple Linear Regression

## explore the data
```{r}
names(Boston)
```
```{r}
Boston[1:5,]
```
```{r}
?Boston
```
## lstat vs medv

lm(y~x,data)
```{r}
lm.fit = lm(medv~lstat, data=Boston)
lm.fit
```
Summary gives us p-values and standard error, as well as the R2 statistic and F-statistic
```{r}
summary(lm.fit)
```
```{r}
names(lm.fit)
```
coeffecients
```{r}
coef(lm.fit)
```
confidence interval
```{r}
confint(lm.fit)
```
predict() can be used to produce confidence intervals and prediction intervals for prediction of medv for a given value of lstat
confidence interval
```{r}
predict(lm.fit, data.frame(lstat=(c(5,10,15))), interval="confidence")
```
prediction interval is substantially wider
```{r}
predict(lm.fit, data.frame(lstat=(c(5,10,15))), interval="prediction")
```

```{r}
attach(Boston)
plot(lstat, medv)
abline(lm.fit)
```
more on abline()
to draw a line with intercept a and slopeb, abline(a,b)
```{r}
plot(lstat, medv)
abline(lm.fit, lwd=3, col="red")

```
```{r}
plot(lstat, medv, pch=20)
plot(lstat, medv, pch="+")
plot(1:20, 1:20, pch=1:20)
```
## diagnostic plots
par() tells R to split the display screen into separate panels
```{r}
par(mfrow=2,2)
plot(lm.fit)
```
residuals() compute the residuals from a linear regression fit
```{r}
plot(predict(lm.fit), residuals(lm.fit))
```
rstudent() returns the studentized residuals
```{r}
plot(predict(lm.fit), rstudent(lm.fit))
```
Leverage statistics can be computed for any number of predictors using the hatvalues()
```{r}
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```
# Multiple Linear Regression
lm(y~x1+x2+x3)
```{r}
mlm.fit = lm(medv~lstat+age)
summary(mlm.fit)
```
# Qualitative Predictor
```{r}
names(Carseats)
```
```{r}
Carseats[1:5,]
```
```{r}
dim(Carseats)
```
# Writing Functions
```{r}
loadLibraries = function(){
  library(ISLR)
  library(MASS)
  print("The libraries are loaded.")
}
```

```{r}
loadLibraries()
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
