---
title: "HW1.problem10(Applied11)"
author: "Guihong Wan"
date: "7/8/2018"
output: html_document
---

```{r}
set.seed(1)
x=rnorm(100)
y=2*x+rnorm(100)

```

## (a)

```{r}
lm.no.out=lm(y~x+0)
summary(lm.no.out)
```
1.The Estimate beta is 1.9939, which is very close to the true value 2.    
2.Std. Error is 0.1065, which is reasonable, since it is close to the mean(rnorm(100))    
3.t statistic is 18.73, which is big.   
4. p value is almost 0. This means we can reject the null hypothesis.    

```{r }
?rnorm
set.seed(1)
print(mean(rnorm(100)))
```

## (b)

```{r}
lm.no.out2=lm(x~y+0)
summary(lm.no.out2)
```
x = y/2-rnorm(100)/2
1.The Estimate beta is 0.39111, which is relatively close to the true value 0.5.    
2.Std. Error is 0.02089. The mean(rnorm(100)/2) is 0.05444368   
3.t statistic is 18.73, which is big.   
4. p value is almost 0. This means we can reject the null hypothesis. 

```{r }
set.seed(1)
print(mean(rnorm(100)/2))
```
## (c)   

1. for(a), the true function is y=2*x+rnorm(100)
for(b), the true function is x = y/2-rnorm(100)/2
2. t statistic is same.
3. Both of p values are small, so we can reject the null hypothesis.

## (d) numerically
```{r }
#for ß'/SE(ß')
beta = 1.9939
s1 = sum((y-x*beta)^2)
s2 = sum((x^2))*99
SE_beta = sqrt(s1/s2)
t_statistic1 = beta/SE_beta

print(t_statistic1) # should be 18.73
```
```{r }
#for later formula
s1 = sqrt(99)*sum(x*y)
s2 = sqrt(sum(x^2)*sum(y^2) - (sum(x*y))^2)

t_statistic2 = s1/s2

print(t_statistic2) # should be 18.73
```
From ablove experiment, we are done.    

### algebraically
Please refere to handwritten part    

##(e)    
Claim:t-statistic for the regression of y onto x is the same as the t-statistic for the regression of x onto y   
Argument: From the second formula, notice that the location of x and y are exchangable, but the value does not change.    

##(f)
```{r}
lm.out=lm(y~x)
summary(lm.out)
```
```{r}
lm.out1=lm(x~y)
summary(lm.out1)
```
From above experiment, t-statistic is 18.556 when lm(y~x); t-statistic is 18.56 when lm(x~y).    
They are almost same.    
